### 2025-01-13 skripsi/chapter4.tex
fix fourier derivatives with periods, fix typos in cover, change judul to lower case and add title case variant, add toc, tof, tot, toa to table of contents, fix font issue with mathptmx, add statement of originality, remove list of notation (for now), fix incorrect statement about burgers eq in ch2, fix sattelite coverage image caption too long, move burgers eq exact solution to ch2, fix figure positioning H not h, reword future work

\subsection{Data Generation: Anti-derivative}
\noindent The first dataset is a simple one dimensional derivative. This was chosen as a simple proof of concept of the ability to solve a differential equation. The equation is related to many real-world problems such as acceleration and speed. One can imagine a train in an ideal world where acceleration is directly translated into speed. When the train accelerates at time \(t \) by some amount \(a \), we can expect the train to have some speed \(u \). In this ideal world, the relationship between speed and acceleration can be modeled with a simple differential \lccref{eq:derivative}. This scenario is found in many real systems albeit often with many more details such as different components of acceleration from friction, drag, gravity, and other factors.
As previously mentioned in \lccref{sec:data_generation}, both velocity \(u \) and acceleration \(a \) are modeled with Fourier series in \lccrefs{eq:fourier_speed,eq:fourier_acceleration} respectively.
\begin{align}
  u\left( t \right)         & = \sum_{k} \hat{u}_k e^{2\pi ikt} \label{eq:fourier_speed}        \\
  a\left( t \right)         & = \sum_{k} \hat{a}_k e^{2\pi ikt} \label{eq:fourier_acceleration}
\end{align}
The domain of the scenario is a two-hour time window. This number was chosen because it is around the ideal length of travel time on high speed rail in comparison to air travel and car travel \autocite{givoniDevelopmentImpactModern2006,wangEfficiencySpatialEquity2019,wrro2236}. This is the first step in generating this dataset.

In the second step, as the derivative \lccref{eq:derivative} does not contain any parameters other than the acceleration which is the input parameter, there are no other parameters to determine. Therefore, the data generation process proceeds to generating coefficients for the speed functions \(\hat{u} \). The coefficients are assigned randomly from a Gaussian distribution with a mean of zero and standard deviation of one. This choice was made such that most wave numbers will have a coefficient of close to zero leaving a sparse set of wave numbers to mostly affect the resulting function. In total, \num{5000} unique functions are generated with \num{100} complex coefficients each.

In the third step, the output function coefficients are computed. To find the relation between \(\hat{u}_k \) and \(\hat{a}_k \), we need to find substitutes for each term in \lccref{eq:derivative}. To do this, we take the derivative of \lccref{eq:fourier_speed} which result in \lccref{eq:fourier_series_derivative}. Using this we can substitute the terms in \lccref{eq:derivative} with \lccrefs{eq:fourier_series_derivative,eq:fourier_acceleration} giving \lccref{eq:example_spectral_method_fourier_substituted}. Finally, after some algebraic manipulation we obtain the relationship between the input \(a^*\) and output function \(u^*\) in terms of their coefficients in \lccref{eq:derivative_coeff}. One also needs to choose the integration constant \(\hat{u}_{0}\) because at \(k=0\) \lccref{eq:derivative_coeff} becomes a division by zero.
\begin{align}
  \dv{u\left( x \right)}{x}                                    & = \sum_{k} \hat{u}_k\times \left( 2\pi ik \right) e^{2\pi ikx} \label{eq:fourier_series_derivative} \\
  \sum_{k} \hat{u}_k\times \left( 2\pi ik \right) e^{2\pi ikx} & = \sum_{k} \hat{a}_k e^{2\pi ikx} \label{eq:example_spectral_method_fourier_substituted}            \\
  \hat{u}_k                                                    & = \hat{a}_k / \left( 2\pi ik \right) \label{eq:derivative_coeff}
\end{align}

@@

The domain of we consider here is based on an exact solution of the equation. This is done so that the learned solver model can be tested on the exact solution. There are a number of sources in literature on the exact solution of the Burgers' equation \autocite{bentonTableSolutionsOnedimensional1972,wazwazPartialDifferentialEquations2010,woodExactSolutionBurgers2006}. In this study, we use a specific solution by \textcite{woodExactSolutionBurgers2006} which can be seen in \lccref{eq:burgers_exact_solution}. This solution is periodic in space but not in time. Therefore, the domain in space will be based on the spatial periodicity of the exact solution which is two. As such, the space domain spans from 0 to 2. The time domain, on the other hand, is chosen to span from 0 to 10 such that enough details of the solution is included.
\begin{equation}
  u(x,t) = \frac{2\nu\pi e^{-\pi^2\nu t}\sin(\pi x)}{a+e^{-\pi^2\nu t}\cos(\pi x)} \label{eq:burgers_exact_solution}
\end{equation}
Continuing to the second step, the parameters involved in \lccref{eq:forced_viscous_burgers} are the viscosity \(\nu \) and the forcing term \(f \). Since the forcing term is dependent on the solution in this step, the only parameter to determine is the viscosity. We choose three constant viscosity values which are \num{0.1}, \num{0.01}, and \num{0.0}. These values are chosen so that a variety of behaviors are represented in the dataset from viscous to inviscid flow.

@@

Next we account for the different viscosity values in this stage. The forcing term is computed using \lccref{eq:forced_viscous_burgers}. The solution field \(u\) and forcing term \(f\) are modeled with Fourier series in \lccrefs{eq:fourier_field,eq:fourier_force} where \(k\) is a vector of spatial and temporal wave number such that \(k_t\) is the temporal wave number and \(k_x\) is the spatial wave number.

@@

  u\left(x, t \right) & = \sum_{k_{x}} \sum_{k_{t}} \hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)} \label{eq:fourier_field} \\
  f\left(x, t \right) & = \sum_{k_{x}}\sum_{k_{t}} \hat{f}_k e^{2\pi i(k_{x}x+k_{t}t)} \label{eq:fourier_force}

@@

Substituting the terms in \lccref{eq:forced_viscous_burgers} with the respective Fourier series, we get the equation \lccref{eq:forced_viscous_burgers_fourier_substitution}. A problem one notices is the nonlinear term \(u\pdv{u}{x}\). A naive approach would multiply all wave numbers terms with each other.

@@

  u\pdv{u}{x} = \left(\sum_{k_{x}} \sum_{k_{t}} \hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)}\right) \times \left(\sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{x})\hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)}\right)

@@

    \sum_{k_{x}} \sum_{k_{t}} \hat{f}_k e^{2\pi i(k_{x}x+k_{t}t)} =
     & \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{t}) \hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)}                                                                \\
     & + \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{x})\hat{uu}_k e^{2\pi i(k_{x}x+k_{t}t)}                                                              \\
     & - \nu\sum_{k_{x}} \sum_{k_{t}} {(2\pi i k_{x})}^2\hat{u}_k e^{2\pi i(k_{x}x+k_{t}t)} \label{eq:forced_viscous_burgers_fourier_substitution}

@@

  \sum_{k_{x}} \sum_{k_{t}} \hat{f}_k & = \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{t}) \hat{u}_k + (2\pi i k_{x})\hat{uu}_k - \nu{(2\pi i k_{x})}^2\hat{u}_k \label{eq:forced_viscous_burgers_fourier} \\
  \hat{f}_k                           & = (2\pi i k_{t}) \hat{u}_k + (2\pi i k_{x})\hat{uu}_k - \nu{(2\pi i k_{x})}^2\hat{u}_k \label{eq:forced_viscous_burgers_coeff}

@@

The exact function \cref{eq:burgers_exact_solution} is computed for each viscosity value. The discrete Fourier transform of the values are then used for doing rollout with the model. For the forcing term, we just use a constant function with a value of zero. The rollout predictions are shown in \lccref{fig:scenario_2_interpretation}. The model is not successful in the rollout for the inviscid equation and for the viscosity of \(\nu=0.01\). Both of these cases, the model produces too much error that the original function is no longer recognizable in the predictions. For the higher viscosity value of \(\nu=0.1\) the rollout produces a recognizable prediction. The error stays to about half the maximum function value. We do see some more noticeable error in the flatter parts of the function. The error also take a very similar shape across the different viscosity values. Since we essentially used the same solutions for training the model for each viscosity, the similarity in error means that it can be alleviated with more diverse training samples. The error for the flatter functions may also be alleviated by including similar flatter functions during training.
\begin{figure}[H]
  \centering
  \begin{adjustwidth}{-0.1\linewidth}{-0.1\linewidth}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_target_0.0.pgf}
      \end{adjustbox}
      \caption{The target for \(\nu=0.0\)}\label{fig:sc2_exact_target_0.0}
    \end{subfigure}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_pred_0.0.pgf}
      \end{adjustbox}
      \caption{The prediction for \(\nu=0.0\)}\label{fig:sc2_exact_pred_0.0}
    \end{subfigure}
    \begin{subfigure}{0.32\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_diff_0.0.pgf}
      \end{adjustbox}
      \caption{The difference for \(\nu=0.0\)}\label{fig:sc2_exact_diff_0.0}
    \end{subfigure}
    \\[0.7\baselineskip]
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_target_0.01.pgf}
      \end{adjustbox}
      \caption{The target for \(\nu=0.01\)}\label{fig:sc2_exact_target_0.01}
    \end{subfigure}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_pred_0.01.pgf}
      \end{adjustbox}
      \caption{The prediction for \(\nu=0.01\)}\label{fig:sc2_exact_pred_0.01}
    \end{subfigure}
    \begin{subfigure}{0.32\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_diff_0.01.pgf}
      \end{adjustbox}
      \caption{The difference for \(\nu=0.01\)}\label{fig:sc2_exact_diff_0.01}
    \end{subfigure}
    \\[0.7\baselineskip]
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_target_0.1.pgf}
      \end{adjustbox}
      \caption{The target for \(\nu=0.1\)}\label{fig:sc2_exact_target_0.1}
    \end{subfigure}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_pred_0.1.pgf}
      \end{adjustbox}
      \caption{The prediction for \(\nu=0.1\)}\label{fig:sc2_exact_pred_0.1}
    \end{subfigure}
    \begin{subfigure}{0.32\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_diff_0.1.pgf}
      \end{adjustbox}
      \caption{The difference for \(\nu=0.1\)}\label{fig:sc2_exact_diff_0.1}
    \end{subfigure}
    % \\[0.7\baselineskip]
  \end{adjustwidth}
  \caption{The rollout predictions for one of the exact function in \lccref{eq:burgers_exact_solution}. The difference is calculated as the targets subtracted by the predictions.}\label{fig:scenario_2_exact}
\end{figure}

>>>>

\subsection{Data Generation: Anti-derivative}
\noindent The first dataset is a simple one dimensional derivative. This was chosen as a simple proof of concept of the ability to solve a differential equation. The equation is related to many real-world problems such as acceleration and speed. One can imagine a train in an ideal world where acceleration is directly translated into speed. When the train accelerates at time \(t \) by some amount \(a \), we can expect the train to have some speed \(u \). In this ideal world, the relationship between speed and acceleration can be modeled with a simple differential \lccref{eq:derivative}. This scenario is found in many real systems albeit often with many more details such as different components of acceleration from friction, drag, gravity, and other factors.
As previously mentioned in \lccref{sec:data_generation}, both velocity \(u \) and acceleration \(a \) are modeled with Fourier series in \lccrefs{eq:fourier_speed,eq:fourier_acceleration} respectively, where \(T\) is the period representing the length of the domain.
\begin{align}
  u\left( t \right) & = \sum_{k} \hat{u}_k e^{2\pi ikt/T} \label{eq:fourier_speed}        \\
  a\left( t \right) & = \sum_{k} \hat{a}_k e^{2\pi ikt/T} \label{eq:fourier_acceleration}
\end{align}
The domain of the scenario is a two-hour time window. This number was chosen because it is around the ideal length of travel time on high speed rail in comparison to air travel and car travel \autocite{givoniDevelopmentImpactModern2006,wangEfficiencySpatialEquity2019,wrro2236}. This is the first step in generating this dataset.

In the second step, as the derivative \lccref{eq:derivative} does not contain any parameters other than the acceleration which is the input parameter, there are no other parameters to determine. Therefore, the data generation process proceeds to generating coefficients for the speed functions \(\hat{u} \). The coefficients are assigned randomly from a Gaussian distribution with a mean of zero and standard deviation of one. This choice was made such that most wave numbers will have a coefficient of close to zero leaving a sparse set of wave numbers to mostly affect the resulting function. In total, \num{5000} unique functions are generated with \num{50} complex coefficients each.

In the third step, the output function coefficients are computed. To find the relation between \(\hat{u}_k \) and \(\hat{a}_k \), we need to find substitutes for each term in \lccref{eq:derivative}. To do this, we take the derivative of \lccref{eq:fourier_speed} which result in \lccref{eq:fourier_series_derivative}. Using this we can substitute the terms in \lccref{eq:derivative} with \lccrefs{eq:fourier_series_derivative,eq:fourier_acceleration} giving \lccref{eq:example_spectral_method_fourier_substituted}. Finally, after some algebraic manipulation we obtain the relationship between the input \(a^*\) and output function \(u^*\) in terms of their coefficients in \lccref{eq:derivative_coeff}. One also needs to choose the integration constant \(\hat{u}_{0}\) because at \(k=0\) \lccref{eq:derivative_coeff} becomes a division by zero.
\begin{align}
  \dv{u\left( t \right)}{t}                                        & = a\left(t\right) \label{eq:fourier_series_derivative}                                                             \\
  \sum_{k} \hat{u}_k\times \left( 2\pi ik/T \right) e^{2\pi ikt/T} & = \sum_{k} \hat{a}_k e^{2\pi ikt/T} \label{eq:example_spectral_method_fourier_substituted}                         \\
  \hat{a}_k                                                        & = \hat{u}_k\left( 2\pi ik/T \right)                                                    \label{eq:derivative_coeff}
\end{align}

@@

The domain of we consider here is based on an exact solution of the equation. This is done so that the learned model can be tested on an exact solution and capture enough of the details within the solution within the domain. In this study, we use a specific solution by \textcite{woodExactSolutionBurgers2006} which can be seen in \lccref{eq:burgers_exact_solution}. This solution is periodic in space but not in time. Therefore, the domain in space will be based on the spatial periodicity of the exact solution which is two. As such, the space domain spans from 0 to 2. The time domain, on the other hand, is chosen to span from 0 to 10 such that enough details of the solution is included.

Continuing to the second step, the parameters involved in \lccref{eq:forced_viscous_burgers} are the viscosity \(\nu \) and the forcing term \(f \). Since the forcing term is dependent on the solution in this step, the only parameter to determine is the viscosity. We choose three constant viscosity values which are \num{0.1}, \num{0.01}, and \num{0.0}. These values are chosen so that a variety of behaviors are represented in the dataset from viscous to inviscid flow.

@@

Next we account for the different viscosity values in this stage. The forcing term is computed using \lccref{eq:forced_viscous_burgers}. The solution field \(u\) and forcing term \(f\) are modeled with Fourier series in \lccrefs{eq:fourier_field,eq:fourier_force} where \(k\) is a vector of spatial and temporal wave number such that \(k_t\) is the temporal wave number and \(k_x\) is the spatial wave number. The period in time is represented by \(T\) and in space it is \(L\).

@@

  u\left(x, t \right) & = \sum_{k_{x}} \sum_{k_{t}} \hat{u}_k e^{2\pi i(k_{x}x/L+k_{t}t/T)} \label{eq:fourier_field} \\
  f\left(x, t \right) & = \sum_{k_{x}}\sum_{k_{t}} \hat{f}_k e^{2\pi i(k_{x}x/L+k_{t}t/T)} \label{eq:fourier_force}

@@

Substituting the terms in \lccref{eq:forced_viscous_burgers} with the respective Fourier series, we get the equation \lccref{eq:forced_viscous_burgers_fourier_substitution}. A problem one notices is the nonlinear term \(u\pdv{u}{x}\). A naive approach would multiply all wave numbers terms with each other as shown in \lccref{eq:burgers_convolution}.

@@

  u\pdv{u}{x} = \left(\sum_{k_{x}} \sum_{k_{t}} \hat{u}_k e^{2\pi i(k_{x}x/L+k_{t}t/T)}\right) \times \left(\sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{x}/L)\hat{u}_k e^{2\pi i(k_{x}x/L+k_{t}t/T)}\right)\label{eq:burgers_convolution}

@@

    \sum_{k_{x}} \sum_{k_{t}} \hat{f}_k e^{2\pi i(k_{x}x/L+k_{t}t/T)} =
     & \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{t}/T) \hat{u}_k e^{2\pi i(k_{x}x/L+k_{t}t/T)}                                                                \\
     & + \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{x}/L)\hat{uu}_k e^{2\pi i(k_{x}x/L+k_{t}t/T)}                                                              \\
     & - \nu\sum_{k_{x}} \sum_{k_{t}} {(2\pi i k_{x}/L)}^2\hat{u}_k e^{2\pi i(k_{x}x/L+k_{t}t/T)} \label{eq:forced_viscous_burgers_fourier_substitution}

@@

  \sum_{k_{x}} \sum_{k_{t}} \hat{f}_k & = \sum_{k_{x}} \sum_{k_{t}} (2\pi i k_{t}/T) \hat{u}_k + (2\pi i k_{x}/L)\hat{uu}_k - \nu{(2\pi i k_{x}/L)}^2\hat{u}_k \label{eq:forced_viscous_burgers_fourier} \\
  \hat{f}_k                           & = (2\pi i k_{t}/T) \hat{u}_k + (2\pi i k_{x}/L)\hat{uu}_k - \nu{(2\pi i k_{x}/L)}^2\hat{u}_k \label{eq:forced_viscous_burgers_coeff}

@@

The exact function \cref{eq:burgers_exact_solution} is computed for each viscosity value. The discrete Fourier transform of the values are then used for doing rollout with the model. For the forcing term, we just use a constant function with a value of zero. The rollout predictions are shown in \lccref{fig:scenario_2_exact}. The model is not successful in the rollout for the inviscid equation and for the viscosity of \(\nu=0.01\). Both of these cases, the model produces too much error that the original function is no longer recognizable in the predictions. For the higher viscosity value of \(\nu=0.1\) the rollout produces a recognizable prediction. The error stays to about half the maximum function value. We do see some more noticeable error in the flatter parts of the function. The error also take a very similar shape across the different viscosity values. Since we essentially used the same solutions for training the model for each viscosity, the similarity in error means that it can be alleviated with more diverse training samples. The error for the flatter functions may also be alleviated by including similar flatter functions during training.
\begin{figure}[H]
  \centering
  \begin{adjustwidth}{-0.1\linewidth}{-0.1\linewidth}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_target_0.0.pgf}
      \end{adjustbox}
      \caption{The target for \(\nu=0.0\)}\label{fig:sc2_exact_target_0.0}
    \end{subfigure}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_pred_0.0.pgf}
      \end{adjustbox}
      \caption{The prediction for \(\nu=0.0\)}\label{fig:sc2_exact_pred_0.0}
    \end{subfigure}
    \begin{subfigure}{0.32\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_diff_0.0.pgf}
      \end{adjustbox}
      \caption{The difference for \(\nu=0.0\)}\label{fig:sc2_exact_diff_0.0}
    \end{subfigure}
    \\[0.7\baselineskip]
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_target_0.01.pgf}
      \end{adjustbox}
      \caption{The target for \(\nu=0.01\)}\label{fig:sc2_exact_target_0.01}
    \end{subfigure}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_pred_0.01.pgf}
      \end{adjustbox}
      \caption{The prediction for \(\nu=0.01\)}\label{fig:sc2_exact_pred_0.01}
    \end{subfigure}
    \begin{subfigure}{0.32\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_diff_0.01.pgf}
      \end{adjustbox}
      \caption{The difference for \(\nu=0.01\)}\label{fig:sc2_exact_diff_0.01}
    \end{subfigure}
    \\[0.7\baselineskip]
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_target_0.1.pgf}
      \end{adjustbox}
      \caption{The target for \(\nu=0.1\)}\label{fig:sc2_exact_target_0.1}
    \end{subfigure}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_pred_0.1.pgf}
      \end{adjustbox}
      \caption{The prediction for \(\nu=0.1\)}\label{fig:sc2_exact_pred_0.1}
    \end{subfigure}
    \begin{subfigure}{0.32\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_diff_0.1.pgf}
      \end{adjustbox}
      \caption{The difference for \(\nu=0.1\)}\label{fig:sc2_exact_diff_0.1}
    \end{subfigure}
    % \\[0.7\baselineskip]
  \end{adjustwidth}
  \caption{The rollout predictions for one of the exact function in \lccref{eq:burgers_exact_solution}. The difference is calculated as the targets subtracted by the predictions.}\label{fig:scenario_2_exact}
\end{figure}

### 2025-01-13 skripsi/chapter5.tex
fix fourier derivatives with periods, fix typos in cover, change judul to lower case and add title case variant, add toc, tof, tot, toa to table of contents, fix font issue with mathptmx, add statement of originality, remove list of notation (for now), fix incorrect statement about burgers eq in ch2, fix sattelite coverage image caption too long, move burgers eq exact solution to ch2, fix figure positioning H not h, reword future work

\section{Conclusion}
% \noindent Bab ini merupakan pamungkas berupa rincian rangkuman yang merupakan simpulan dari analisis yang telah dilakukan. Simpulan ini menyajikan sejumlah hal penting yang disampaikan secara ringkas, padat, dan utuh, yang menjawab tujuan penelitian yang dituliskan pada Bab Pendahuluan. Sangat mungkin   ada beberapa konsekuensi dan implikasi yang ditimbulkan dari simpulan yang dihasilkan, yang sepatutnya menjadi perhatian pada penelitian berikutnya. Judul bab dapat disesuaikan, namun umumnya ada \textit{Simpulan} yang memang mendominasi isi bab ini.

\section{Future Work}
% \noindent Sejumlah ide yang muncul ketika melaksanakan penelitian TA dapat menjadi bahan atau topik untuk pekerjaan selanjutnya. Hal ini dapat berupa perbaikan atau ragam lain dari apa yang telah dilakukan sepanjang penelitian. Sub bab ini menjadi sumber informasi penting bagi, utamanya mahasiswa, yang akan melakukan penelitian lanjutan.

>>>>

\section{Conclusion}
\noindent Based on the results of the research into \MakeLowercase{\judul}, several conclusions can be drawn.
\begin{enumerate}
    \item The proposed SpectralSVR model is able to learn the relationships defined by PDEs. This is done with a computational model that with four phases which are data preparation, data transformation, model training, and finally model evaluation.
    \item Interpretation of the proposed model can be done to a certain extent using two tools which are the correlation image and p-matrix developed by \textcite{ustunVisualisationInterpretationSupport2007}.
    \item The proposed model is also capable in dealing with noise and partial data as shown in scenario 1 and 3.
    \item The model's capabilities are also verified using exact solution. This revealed that for some configurations the model is able to successfully generalize to exact solutions.
\end{enumerate}
% \noindent Bab ini merupakan pamungkas berupa rincian rangkuman yang merupakan simpulan dari analisis yang telah dilakukan. Simpulan ini menyajikan sejumlah hal penting yang disampaikan secara ringkas, padat, dan utuh, yang menjawab tujuan penelitian yang dituliskan pada Bab Pendahuluan. Sangat mungkin   ada beberapa konsekuensi dan implikasi yang ditimbulkan dari simpulan yang dihasilkan, yang sepatutnya menjadi perhatian pada penelitian berikutnya. Judul bab dapat disesuaikan, namun umumnya ada \textit{Simpulan} yang memang mendominasi isi bab ini.

\section{Future Work}
During the work on this study, some limitations were imposed, and many new questions also went unanswered. Here, we would like to list some potential avenues for future work:
\begin{itemize}
    % TODO: reword these points
    \item The synthetic data used in scenarios 1 and 2 were generated using MMS\@. While mathematically correct, this data is not realistic. Incorporating more realistic data from traditional numerical methods or other sources could enhance the model's ability to predict more realistic solutions.
    \item Test how the auto-regression of weather compares to the target data.
    \item Compare inverse prediction results with traditional derivatives, such as the spectral method or FDM\@.
    \item Compare the proposed method with other methods in comparable situations.
    \item Measure and compare the efficiency (time) of computing solutions against traditional and machine learning-based methods.
    \item Add more basis functions, such as spherical harmonics or wavelet bases.
    \item Incorporate more regression models, specifically more support vector regression models, to continue utilizing the correlation image and p-matrix.
    \item Use better metrics for measuring performance, such as the \enquote{standard error of regression}.
    \item Analyze the performance with different hyperparameters or data sizes and present the results in charts.
    \item Perform an analysis of the error by wave number.
    \item Solve the problem of double penalties that cause the model to favor smooth solutions \autocite{brownForecastsSpatialFields2011,NIPS2017_44a2e080}. Try using stronger regularization (a higher regularization parameter) for higher wave numbers.
    \item Add support for sparse data by employing data assimilation techniques, such as the Lomb-Scargle periodogram \autocite{vanderplasUnderstandingLombScargle2018}, and 4D-Var data assimilation \autocite{puNumericalWeatherPrediction2018,parkDataAssimilationAtmospheric2013}.
    \item Study the contribution patterns for different terms in a PDE using the p-matrix or other methods.
\end{itemize}
% \noindent Sejumlah ide yang muncul ketika melaksanakan penelitian TA dapat menjadi bahan atau topik untuk pekerjaan selanjutnya. Hal ini dapat berupa perbaikan atau ragam lain dari apa yang telah dilakukan sepanjang penelitian. Sub bab ini menjadi sumber informasi penting bagi, utamanya mahasiswa, yang akan melakukan penelitian lanjutan.

### 2025-01-13 skripsi/identitas.tex
change to biblatex, start background
research design and computational model, fix root file latex
Finish ch4, fix some problems with
finish ch2 and start ch5
fix fourier derivatives with periods, fix typos in cover, change judul to lower case and add title case variant, add toc, tof, tot, toa to table of contents, fix font issue with mathptmx, add statement of originality, remove list of notation (for now), fix incorrect statement about burgers eq in ch2, fix sattelite coverage image caption too long, move burgers eq exact solution to ch2, fix figure positioning H not h, reword future work

%isi identitas diri di file ini......
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%JUDUL: 
\providecommand{\judul}{
    APROKSIMASI SOLUSI \textit{PARTIAL DIFFERENTIAL EQUATIONS} DENGAN \textit{PHYSICS-INFORMED SUPPORT VECTOR MACHINE}
}
%PENULIS:
\providecommand{\penulis}{
    Ahmad Izzuddin
}
%NIM:
\providecommand{\nim}{
    1908919
}

%Pembimbing1 dan pembimbing2, misalnya:
%Pembimbing 1
\providecommand{\pembimbingsatu}{
    Prof. Dr. Lala Septem Riza, M.T.
}
%NIP Pembimbing 1:
\providecommand{\NIPpbbsatu}{
    197809262008121001
}
%Pembimbing2
\providecommand{\pembimbingdua}{
    Nama Pembimbing 2
}
%NIP Pembimbing 2:
\providecommand{\NIPpbbdua}{
    314159265358979323
}

%untuk keywords yang ada di abstrak, di sini:
\providecommand{\katakunci}{
    Konsep Abstrak, Komponen Abstrak, Kata Kunci.
}
\providecommand{\keywords}{
    Abstract Concepts, Abstract Components, Key Words.
}

>>>>

% !TEX root = ./skripsi.tex
%isi identitas diri di file ini......
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%JUDUL: 
\providecommand{\judul}{approximating solutions of governing equations with Fourier transform and support vector machine}
\providecommand{\judulcapitalized}{Approximating Solutions of Governing Equations With Fourier Transform and Support Vector Machine}
%PENULIS:
\providecommand{\penulis}{Ahmad Izzuddin}
%NIM:
\providecommand{\nim}{1908919}

%Pembimbing1 dan pembimbing2, misalnya:
%Pembimbing 1
\providecommand{\pembimbingsatu}{Prof.\ Dr.\ Lala Septem Riza, M.T.}
%NIP Pembimbing 1:
\providecommand{\NIPpbbsatu}{197809262008121001}
%Pembimbing2
\providecommand{\pembimbingdua}{Dr.\ Muhammad Nursalman, M.T.}
%NIP Pembimbing 2:
\providecommand{\NIPpbbdua}{197909292006041002}

%untuk keywords yang ada di abstrak, di sini:
\providecommand{\katakunci}{\textit{Operator Learning}, PDE, LSSVM.}
\providecommand{\keywords}{Operator Learning, PDE, LSSVM.}
